### 2022-07-20 paper/localpsf.tex
add missing impulse response files

We may reduce the average cost of performing ellipsoid intersection tests by first checking whether the coordinate axis aligned bounding boxes for the ellipsoids intersect. If the bounding boxes do not intersect, then the ellipsoids do not intersect, so no further action is necessary. If the bounding boxes intersect, the ellipsoids might intersect, or they might not intersect, so one must perform the complete ellipsoid intersection test described in Section \ref{sec:fast_ellipsoid_intersection_test}.

The ellipsoid 
$
E = \{x : (x - \spatialmean)^T \spatialcov^{-1} (x - \spatialmean) \le \tau^2\}
$
is bounded by the box
\begin{equation*}
	\prod_{i=1}^\gdim \left[ \spatialmean_i -\sqrt{\Sigma_{ii}}/\tau, \spatialmean_i +\sqrt{\Sigma_{ii}}/\tau \right],
\end{equation*}
where $\Sigma_{ii}$ is the $i$th diagonal entry of $\Sigma$\footnote{See \url{https://math.stackexchange.com/q/3928964}}. The boxes
\begin{equation*}
	\prod_{i=1}^\gdim \left[a_i^-, a_i^+\right], \quad \text{and} \quad \prod_{i=1}^\gdim \left[b_i^-, b_i^+\right]
\end{equation*}
intersect if and only if $a_i^- \le b_i^+$ and $b_i^- \le a_i^+$ for $i=1,\dots,d$\footnote{See \url{https://stackoverflow.com/a/65107290/484944}}.

>>>>

One may reduce the average cost of performing ellipsoid intersection tests by first checking whether the coordinate axis aligned bounding boxes for the ellipsoids intersect. If the bounding boxes do not intersect, then the ellipsoids do not intersect, so no further action is necessary. If the bounding boxes intersect, the ellipsoids might intersect, or they might not intersect, so one must perform the complete ellipsoid intersection test described in Section \ref{sec:fast_ellipsoid_intersection_test}.

The smallest coordinate axis aligned box that contains the ellipsoid 
$
E = \{x : (x - \spatialmean)^T \spatialcov^{-1} (x - \spatialmean) \le \tau^2\}
$
is given as follows:
\begin{equation*}
	\prod_{i=1}^\gdim \left[ \spatialmean_i -\tau\sqrt{\Sigma_{ii}}, \spatialmean_i +\tau\sqrt{\Sigma_{ii}} \right],
\end{equation*}
where $\Sigma_{ii}$ is the $i$th diagonal entry of $\Sigma$\footnote{See \url{https://math.stackexchange.com/q/3928964}}. The boxes
\begin{equation*}
	\prod_{i=1}^\gdim \left[a_i^-, a_i^+\right], \quad \text{and} \quad \prod_{i=1}^\gdim \left[b_i^-, b_i^+\right]
\end{equation*}
intersect if and only if $a_i^- \le b_i^+$ and $b_i^- \le a_i^+$ for $i=1,\dots,d$.
